Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-03 paper/ms.tex
Update multi-orbit text, update terminology and numbers

We now repeat the procedure but continuously changing the error in the assumed
midplane. In Figure~\ref{fig:many_orbit_wrong_ref}, we report the 95\uth minus
5\uth percentile divided by the true action value for three different orbits.
The red orbit is exactly the same as in Figure~\ref{fig:one_orbit_wrong_ref},
and we also consider two more planar orbits with initial vertical velocities
of $30\,\kms$ (\Gus{orange}) and $10\,\kms$ (\Gus{blue}). For these two new
orbits, the true actions are $(J_r, L_z, J_z) = (37.9, -1520, 7.0)\,\actunit$
and $(40.4, -1520, 0.7)\,\actunit$ for the \Gus{orange} and \Gus{blue} orbits,
respectively. The value of $z_{\text{max}}$ for these orbits are $122\,\pc$
and $425\,\pc$, respectively (with the blue orbit having $z_{\text{max}}$ of
$854\,\pc$.) \Gus{Easy way to explain change in $J_r$?}

The top row of Figure~\ref{Fig:many_orbit_wrong_ref} shows the error in each
action assuming an offset in the midplane. In the {\em bottom row} we also
consider offsets in the Galactocentric radius $R$. The {\em left}, {\em
middle}, and {\em right} columns show the 95\uth minus 5\uth percentile of the
measured action over the course of the incorrect orbit divided by the true
action value as a percentage.

In the {\em upper middle} panel, there is essentially no error in the
determination of $L_z$. This is expected since, in principle, $L_z$ only
depends on the $x$- and $y$-components of the position and velocity of the
stars\footnote{Though this is not how we compute $L_z$ in practice.}, and is
thus unaffected by offsets in $z$.

@@

For completeness, we also consider the effect of offsets in the Galactocentric
radius $R$ in the {\em bottom panels}. The error is largest for $J_r$, with
some deviations resulting in $L_z$ and relatively small deviations in $J_z$.
In the {\em bottom left} panel the orange and blue lines overlap, and in the
{\em bottom middle} and {\em bottom right} panels all three lines overlap.

>>>>

We now repeat the procedure but continuously changing the error in the $z$ and
$x$ components. In Figure~\ref{fig:many_orbit_wrong_ref}, we report the 95\uth
minus 5\uth percentile divided by the true action value for three different
orbits. The \Gus{orange} orbit is exactly the same as in
Figure~\ref{fig:one_orbit_wrong_ref}, and we also consider two more planar
orbits with initial vertical velocities of $50\,\kms$ (\Gus{red}) and
$10\,\kms$ (\Gus{blue}). For these two new orbits, the true actions are $(J_r,
L_z, J_z) = (32.6, -1520, 22.9)\,\actunit$ and $(40.4, -1520, 0.7)\,\actunit$
for the \Gus{red} and \Gus{blue} orbits, respectively. The value of
$z_{\text{max}}$ for these orbits are $854\,\pc$ and $122\,\pc$, respectively
(with the orange orbit having $z_{\text{max}}$ of $425\,\pc$.) \Gus{Easy way
to explain change in $J_r$?}

The top row of Figure~\ref{Fig:many_orbit_wrong_ref} shows the error in each
action assuming an offset in the $z$ component (i.e. the Galactic midplane).
In the {\em bottom row} we also consider offsets in the $x$ component (i.e.
the Solar radius). The {\em left}, {\em middle}, and {\em right} columns show
the relative error in $J_z$, $L_z$, and $J_r$, respectively. We compute the
relative error as the  95\uth minus 5\uth percentile of the measured action
($\Delta J_i$) over the course of the first $\Gyr$ of the incorrectly observed
orbit divided by the true action value as a percentage.

In the {\em upper middle} panel, there is essentially no error in the
determination of $L_z$. This is expected since, in principle, $L_z$ only
depends on the $x$- and $y$-components of the position and velocity of the
stars\footnote{Though this is not how we compute $L_z$ in practice.}, and is
thus unaffected by offsets in $z$. This also agrees with the result we found
in Figure~\ref{fig:one_orbit_wrong_ref}.

@@

For the offset in the Solar radius {\em bottom panels}, the error is largest
for $J_r$, with some deviations resulting in $L_z$ and relatively small
deviations in $J_z$. In the {\em bottom left} panel the orange and blue lines
overlap, and in the {\em bottom middle} and {\em bottom right} panels all
three lines overlap.
